Denotational Semantics of General Payment Primitives, and Its Payment System

### 2022-10-04 packages/spec-haskell/yellowpaper/Paper1.tex
change article outline style and biblatex style

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{Introduction}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

In Chapter 2, we shall first explore the foundation for the survey. Here we present a formal
definition of payment system and its components. We then select a few relevant approaches used in
computer science useful for modeling and defining formal specification for the payment system.

One of the approaches is \textit{denotational semantics}, which is used in Chapter 3 of the paper to
define the general payment primitives. Along with the denotational semantics, a
restatement\footnote{It is a borrowed term from common law: ``restatement of the law''. In our case,
the denotative mathematical laws.} of it in \textit{Haskell programming language}
(\cite{hudak1992report} \cite{jones2003haskell} \cite{marlow2010haskell}) is also included.

In Chapter 4, a reference implementation of the general payment primitives and its payment system
called \textit{Superfluid Protocol} is introduced.

In Chapter 5, some possible further investigations are also included as notes.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{Foundation}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

A representation of money and its distribution proposed in \cite{buldas2021unifying} involves the
following components:

@@

This discrete nature of this money distribution model is schematically depicted
in~\ref{fig:discrete-md}:

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{General Payment Primitives}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{Superfluid Protocol - A Reference Implementation}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\begin{figure}[p]
    \centering
    \includegraphics[width=0.9\textwidth]{../assets/agreement-data-structures.png}
    \caption{Agreement Data Structures}
    \label{fig:ac-agreement-data-structures}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{Final Words}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Notes on Future Investigations}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Restatement in Agda, Correctness and Equivalence Proofs}

@@

\subsection{Future Papers on Modern Payment System}

@@

\subsection{General Accounting Domains \& Real Time Finance}

@@

\section{Conclusions}
%%%%%%%%%%%%%%%%%%%%%

@@

@@

\section{Acknowledgments}
%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

\part*{Introduction}
%%%%%%%%%%%%%%%%%%%%%%

@@

In part\ref{part:foundation}, we shall first explore the foundation for the survey. Here we present
a formal definition of payment system and its components. We then select a few relevant approaches
used in computer science useful for modeling and defining formal specification for the payment
system.

One of the approaches is \textit{denotational semantics}, which is used in part \ref{part:gpp} of
the paper to define the general payment primitives. Along with the denotational semantics, a
restatement\footnote{It is a borrowed term from common law: ``restatement of the law''. In our case,
the denotative mathematical laws.} of it in \textit{Haskell programming language}
(\cite{hudak1992report} \cite{jones2003haskell} \cite{marlow2010haskell}) is also included.

In part \ref{part:sf}, a reference implementation of the general payment primitives and its payment
system called \textit{Superfluid Protocol} is introduced.

Notes on possible further investigations are also included in the end of the paper.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\part{Foundation}\label{part:foundation}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

A representation of money and its distribution proposed in ``a unifying theory''
from \citeauthor{buldas2021unifying} involves the following components:

@@

This discrete nature of this money distribution model is schematically depicted
in figure \ref{fig:discrete-md}:

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\part{General Payment Primitives}\label{part:gpp}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\part{Superfluid Protocol - A Reference Implementation}\label{part:sf}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.9\textwidth]{../assets/agreement-data-structures.png}
    \caption{Agreement Data Structures}
    \label{fig:ac-agreement-data-structures}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\part*{Notes on Future Investigations}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Restatement in Agda, Correctness and Equivalence Proofs}

@@

\section{Future Papers on Modern Payment System}

@@

\section{General Accounting Domains \& Real Time Finance}

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\part*{Conclusions}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\part*{Acknowledgments}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
